Visually pleasing knot projections

### 2021-09-15 inst/jma_rebuttal.tex

P2, line 43: ``uniform" curvature is not possible, since many knots
have inflection points.  It is better to ask for 'smoothly changing'
curvature, and to limit maximal curvature.

\textcolor{blue}{Corrected:
  \begin{description}
  \item[OLD text] Curvature to be as uniform as possible
\item[NEW text] Curvature to be as smoothly changing as possible, with
  limited maximal curvature
  \end{description}
}

P2, line 46: What does it mean for symmetry to be ``present" in the
knot?

\textcolor{blue}{
  \begin{description}
  \item[OLD text] Any symmetry present in the knot should be enforced exactly, and be visually apparent
\item[NEW text] Any symmetry desired in the knot should be enforced exactly, and be visually apparent
  \end{description}
}

@@

Figure 2:  Specify what order Bezier curves are being used.

P4, line 18: A gentle introduction to ``R" would help to make the
following easier to understand.

P4, lines 27-32: What is the meaning of this? - Six points defining
two handle pairs?  (Why the extreme precision with 8 digits?)

\textcolor{blue}{Only the first six lines are shown for brevity, I have
  changed the text accordingly: ``Above we see only the first six lines
of the object"}

### 2021-09-16 inst/jma_knot.tex
fixes #21
fixes #34

\begin{itemize}
\item Curvature to be as smoothly changing as possible, with limited maximal curvature
\item Strands to cross at right angles
\item Crossing points to be separate from one another
\item Any symmetry present in the knot should be enforced exactly, and be visually apparent
\end{itemize}

Knot diagrams may be created using vectorized graphics software such
as inkscape~\cite{kirsanov2009}: one specifies a sequence of control
points, then interpolates between these points to create a knot
diagram with the appropriate topology (inkscape is a widely-used
system available under the GPL).  One way of smoothly interpolating
between specified points is Bezier curves~\cite{olsen2014}.  A Bezier
curve is a visually pleasing polynomial path that can be used to
specify the path of a knot projection.

The software discussed here~\cite{hankin2020} allows one to specify a
knot in terms of its Bezier control points within inkscape, import the
object into R~\cite{rcore2016}, and then to use numerical optimization
techniques to improve the visual appearance of the knot.

>>>>

\begin{itemize}
\item Curvature to be as smoothly changing as possible, with limited maximal curvature
\item Strands to cross at right angles
\item Crossing points to be separate from one another
\item Any symmetry desired in the knot should be enforced exactly, and be visually apparent
\end{itemize}

Knot diagrams may be created using vectorized graphics software such
as inkscape~\cite{Inkscape}: one specifies a sequence of control
points, then interpolates between these points to create a knot
diagram with the appropriate topology (inkscape is a widely-used
system available under the GPL).  One way of smoothly interpolating
between specified points is Bezier curves~\cite{olsen2014}.  A Bezier
curve is a visually pleasing polynomial path that can be used to
specify the path of a knot projection.

The software discussed here~\cite{hankin2020} allows one to specify a
knot in terms of its Bezier control points within inkscape, import the
object into R~\cite{rcore2021}, and then to use numerical optimization
techniques to improve the visual appearance of the knot.
